JLyrics \titlenote{Submitted as the final project for CS 410 Summer 2014.}

### 2014-08-03 report/paper.tex
Report: Added citations.

@@

As time went on, a new standard of expressing characters as strings of bytes appeared called Unicode. It proposed blueprints of how one should represent characters form any and all alphabets in a set length of bits. Unicode is an abstract concept. The most popular encoding of Unicode to this day is UTF-8 (Unicode Transformation Format 8). Many Japanese developers are content with Shift-JIS even though the Shift-JIS encoding can't handle non-Japanese and non-Latin characters, so there is a struggle involved with dealing with Japanese text such that one must check if the text was encoded in Shift-JIS, UTF-8, or something else.

@@

What similar things are already out there? You can cite things like
this~\cite{manning-ir-book} and this~\cite{zhai-smoothing}. I got the second
reference bibtex from \url{http://dl.acm.org/citation.cfm?id=984322}. I just
simplified the bibtex reference names to ``manning-ir-book'' and
``zhai-smoothing''. Also, did you notice that URL and citations were clickable?

@@

%\bibliographystyle{plain}
%\bibliography{bib} % "bib" is the name of the .bib file

>>>>

\section{Indexing and Searching}

A search engine will have nothing to search for if the docs are not indexed. Everyone in CS 410 had the background required to build a search engine, but for the summer semester, there was not enough time to implement an indexer and a searcher. In order to alleviate this and allow us to understand search engines in general, the professor had us all do week-long homework problems using a program he developed. This program, Goose, was a Java application built around Lucene. Lucene is an API for implementing an indexer and a searcher. In order to save development time, we used Goose as the base to JLyrics.

Goose was built to work with English text, so it would not work with our data set right out of the box. The only change we had to make was to discover how to replace the self-made text analyzer in Goose with a JapaneseAnalyzer that comes with Lucene. This JapaneseAnalyzer was a library originally called Kuromoji. Kuromoji was donated to Lucene and became a part of Lucene's API \cite{kuromoji-donate}. Using JapaneseAnalyzer, we were able to create a working indexer and searcher.

@@

As time went on, a new standard of expressing characters as strings of bytes appeared called Unicode. It proposed blueprints of how one should represent characters form any and all alphabets in a set length of bits. Unicode is an abstract concept \cite{unicode-abstract}. The most popular encoding of Unicode to this day is UTF-8 (Unicode Transformation Format 8). Many Japanese developers are content with Shift-JIS even though the Shift-JIS encoding can't handle non-Japanese and non-Latin characters, so there is a struggle involved with dealing with Japanese text such that one must check if the text was encoded in Shift-JIS, UTF-8, or something else.

@@

In terms of related work, Anime Lyrics dot Com did precisely what we have attempted to do. Their site conglomerates Japanese music lyrics from multiple venues so that users can search for lyrics in Japanese, romaji, or English. The amount of data they have is proportional to the amount of manpower put into the site. We wanted to have a more automated system so that people could stay up-to-date with popular music scenes such as Vocaloid music uploaded to Piapro or Touhou remix music detailed on the Touhou Doujin CD no Kashi Wikipedia site. To that extent, we could arguably state that we are following in the footsteps of Anime Lyrics dot Com while simultaneously using their work.

%What similar things are already out there? You can cite things like this~\cite{manning-ir-book} and this~\cite{zhai-smoothing}. I got the second reference bibtex from \url{http://dl.acm.org/citation.cfm?id=984322}. I just simplified the bibtex reference names to ``manning-ir-book'' and ``zhai-smoothing''. Also, did you notice that URL and citations were clickable?

@@

\bibliographystyle{plain}
\bibliography{bib} % "bib" is the name of the .bib file
